### 2015-11-08 ch02-qlogms/logMS_IMTC.tex
Add misalignmet figure to qlogms
Add some operators

  Each decade that is completely  within the resulting set of excited frequencies $\set{f_1, \ldots, f_F}$ contains
   \begin{equation}
     \floor{\frac{\log (10 f) - \log( f )}{\log \alpha}}
         = \floor{\log_{\alpha} 10}
   \end{equation}
   excited frequency lines. 
   I.e. the same number of frequency components is present per decade, such that the power in each decade is identical when a constant amplitude spectrum ($A_k = A_{\mathrm{in}}$) is used.
   Obviously, the same argument can be held for any relative bandwidth (e.g. octave or even the $\wdB$ of a particular system).

@@

  \subsection{Setup for selecting $\alpha$}
  When we now take a closer look at the general second order system \eqref{eq:secondOrderSystemCT}, we still are left with $\dc$ and $\damping$ as free parameters in the prototypes.
  Note that $\dc$ is a scaling factor for the FRF.
  Hence the results for different values of $\dc$ only differ by a scaling factor.
  So we only need to perform the analysis for a fixed value of $\dc$, which was chosen equal to $1$ in our test case.

@@

  Instead of using \eqref{eq:theoreticalBestVariationOmega} to establish the influence of the resonance frequency, we apply an equivalent approach that is more intuitive to interpret.
  \TODO{show $\alpha$ and $\beta$ graphically (cfr. poster)}
  We choose the resonance frequency of the systems such that
  \begin{equation}
   \wM\left( \wn \right)  = \omega_k + \beta \left( \omega_{k+1} - \omega_k \right)
   \text{ with } 0 \leq \beta < 1
   \label{eq:chosenVariationOmega}
  \end{equation}
  where $\omega_k$ and $\omega_{k+1}$ are the excited grid lines closest to the frequency $\wM$ where the FRF has its peak amplitude and $\beta$ is the misalignment coefficient that is varied over the interval $[0,1]$.
  This means that $\omega_k \leq \wM \leq \omega_{k+1}$ and that $\beta$ replaces the $\gamma$ factor in \eqref{eq:theoreticalBestVariationOmega}.
  If we take a look at the special case when $\beta=0$ (or $\beta=1$) in this expression, we see that this situation occurs when the peak value of the FRF at $\wM$ coincides with the grid line $\omega_k$ or $\omega_{k+1}$ respectively.
  Basically, we study second order systems whose peak frequency $\wM$ is shifted between two neighboring excited frequency lines.
  From the previous section, we know that the exact frequency matters little as long as it remains within the bulk of the frequency grid.
  In this particular example $\wn$ was chosen at approximately $1 \unit{rad/s}$.

>>>>

  \begin{property}
    Each decade that is completely  within the range of excited frequencies $\set{f_1, \ldots, f_F}$ contains
   \begin{equation}
     F_{\decade} \isdef
     \floor{\frac{\log (10 f) - \log( f )}{\log \alpha}}
         = \floor{\log_{\alpha} 10}
   \end{equation}
   excited frequency lines.
   I.e. the same number of frequency components is present per decade, such that the power in each decade is identical when a constant amplitude spectrum ($A_k = A_{\mathrm{in}}$) is used.
  \end{property}

   Obviously, the same argument can be held for any relative bandwidth (e.g. octave or even the $\wdB$ of a particular system).

@@

  \subsection{Selection of the frequency grid spacing $\alpha$}
  When we now take a closer look at the general second order system \eqref{eq:secondOrderSystemCT}, we still are left with $\dc$ and $\damping$ as free parameters in the prototypes.
  Note that $\dc$ is a scaling factor for the FRF.
  Hence the results for different values of $\dc$ only differ by a scaling factor.
  So we only need to perform the analysis for a fixed value of $\dc$, which was chosen equal to $1$ in our test case.

@@

  Instead of using \eqref{eq:theoreticalBestVariationOmega} to establish the influence of the resonance frequency, we apply an equivalent approach that is more intuitive to interpret.

  \begin{figure}
    \centering
    \setlength\figureheight{5cm}
    \setlength\figurewidth{0.8\columnwidth}
    \input{\thisDir/figs/misalign.tikz}
    \caption[Depiction of the grid misalignment $\beta$ for a logarithmic generalized multisine.]{Graphical depiction of the misalignment coefficient $\beta$ with respect to a logarithmic frequency grid with spacing $\alpha$ for two systems with different damping.
    The }
    \label{fig:misalignment-logms}
  \end{figure}

  We choose the resonance frequency of the systems such that
  \begin{equation}
   \wM\left( \wn \right)  = \omega_k + \beta \left( \omega_{k+1} - \omega_k \right)
   \text{ with } 0 \leq \beta < 1
   \label{eq:chosenVariationOmega}
  \end{equation}
  where $\omega_k$ and $\omega_{k+1}$ are the excited grid lines closest to the frequency $\wM$ where the FRF has its peak amplitude and $\beta$ is the misalignment coefficient that is varied over the interval $\RightOpenInterval{0,1}$ as depicted graphically in \figref{fig:misalignment-logms}
  This means that $\omega_k \leq \wM \leq \omega_{k+1}$ and that $\beta$ replaces the $\gamma$ factor in \eqref{eq:theoreticalBestVariationOmega}.
  If we take a look at the special case when $\beta=0$ (or $\beta=1$) in this expression, we see that this situation occurs when the peak value of the FRF at $\wM$ coincides with the grid line $\omega_k$ or $\omega_{k+1}$ respectively.
  Basically, we study second order systems whose peak frequency $\wM$ is shifted between two neighboring excited frequency lines.
  From the previous section, we know that the exact frequency matters little as long as it remains within the bulk of the frequency grid.
  In this particular example $\wn$ was chosen at approximately $1 \unit{rad/s}$.

### 2015-11-08 config/glossaries.inc.tex
Add some operators

%% SYMBOLS
\newsymbolglos{0-placeholder}{\placeholder}{Placeholder symbol}

@@

\newsymbolglos{operator-exp}{\expval{\placeholder}}{Expected value of \placeholder}
\newsymbolglos{operator-pinv}{\pinv{\placeholder}}{Moore-Penrose pseudo-inverse of the matrix \placeholder}
\newsymbolglos{operator-tran}{\placeholder^{\TT}}{Transpose of the matrix \placeholder}
\newsymbolglos{operator-ht}{\placeholder^{\HT}}{Hermitian transpose of the matrix \placeholder}

>>>>

%% SYMBOLS
% \newsymbolglos{0-placeholder}{\placeholder}{Placeholder symbol}

@@

\newsymbolglos{matrix-eye}{\I_n}{ $n \times n$ identify matrix }

\newsymbolglos{operator-exp}{\expval{\placeholder}}{Expected value of \placeholder}
\newsymbolglos{operator-pinv}{\pinv{\placeholder}}{Moore-Penrose pseudo-inverse of the matrix \placeholder}
\newsymbolglos{operator-tran}{\placeholder^{\TT}}{Transpose of the matrix \placeholder}
\newsymbolglos{operator-ht}{\placeholder^{\HT}}{Hermitian transpose of the matrix \placeholder}
\newsymbolglos{operator-round-floor}{\floor{\placeholder}}{\placeholder{} rounded downwards (\code{floor})}
\newsymbolglos{operator-round-ceil}{\ceil{\placeholder}}{\placeholder{} rounded upwards (\code{ceil})}
\newsymbolglos{operator-round-round}{\round{\placeholder}}{\placeholder{} rounded towards the nearest integer (\code{round})}
